%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
Web developer since the availability of the Internet in Belgium (20 years ago, when Microsoft FrontPage and Adobe Dreamweaver were a thing). I quickly moved to dynamic programming languages like PHP to build dynamic websites more commonly named CMS today (no-no WordPress didn't exist at that time).

I have a degree in computer sciences. I like to constantly grow my knowledge and experience \Rightarrow  I'm not afraid to learn something new. 

I've architected, developed (from end-to-end), put in production, maintained, and provided end-user support for multiple projects in numerous technologies like Java / Python / HTML / CSS / JavaScript / SQL / InterSystems Caché and the HL7 standards for healthcare data. Take a look at the \emph{Projects} section for some examples of projects I've contributed to.

Working in a medical environment for 13 years lead me to work on HL7 integration interfaces multiple times. For these projects, I had to manipulate, integrate and exchange health information based on HL7 v2.x standards by building medical software and by using the InterSystems HealthShare platform.

I'm agile as I can work on multiple constantly evolving and changing projects at the same time.

Love to code and design great quality user-friendly software.
To me, ICT is a way to make people's lives easier.
\end{cvparagraph}
